Reach OPT MSNA 2021

### 2021-06-30 MSNA_2021_Monitoring_report.Rmd
update on the cleaning scripts

# survey length by enumerator

survey_length <- df %>% 
    filter(df$consent == "yes") %>% 
  group_by(Enumerator = enumerator_num) %>% 
  dplyr::summarise(
    Median_duration = round(median(as.numeric(df$interview_duration), na.rm = T),0)
  ) %>% 
  arrange(desc(Median_duration) )

@@

# Enumerator with short interv duration
short_interviews_by_enum <- df %>% 
  filter(df$consent == "yes" ) %>% 
  dplyr::filter(interview_duration < time_limit & today > "2021-06-15") %>%

@@

>>>>

survey_len <- df %>% 
  filter(consent == "yes" & enumerator_num == "1") %>% 
  dplyr::select(interview_duration)
# survey length by enumerator
survey_length <- df %>% 
    filter(df$consent == "yes") %>% 
  group_by(Enumerator = enumerator_num) %>% 
 summarise(
    Median_duration = round(median(as.numeric(interview_duration), na.rm = T),0)
  )%>% 
  dplyr::arrange(desc(Median_duration) )

@@

# Enumerator with short interv duration
short_interviews_by_enum <- df %>% 
  dplyr::filter(df$consent == "yes" ) %>% 
  dplyr::filter(interview_duration < time_limit & today > "2021-06-15") %>%

@@

## Productivity
